The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-11-21 paper/ms.tex
remove rubric
indigenous acknowledgement

Considering stars lying close to the main sequence, from the \kepler power spectrum we identify solar-like oscillations in HD~182354 and HD~176209 at frequencies consistent with them being subgiants or contaminated with flux from red giants. \textcolor{red}{Get frequencies}.

@@

\textcolor{red}{Ashley/Dan/Vichi?}

@@

BP acknowledges being on the traditional territory of the Lenape Nations and recognizes that Manhattan continues to be the home to many Algonkian peoples. We give blessings and thanks to the Lenape people and Lenape Nations in recognition that we are carrying out this work on their indigenous homelands. We would like to acknowledge the Gadigal people of the Eora Nation and the Norongerragal and Gweagal peoples of the Tharawal Nation as the traditional owners of the land at the University of Sydney and the Sutherland Shire on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.

>>>>

Considering stars lying close to the main sequence, from the \kepler power spectrum we identify solar-like oscillations in HD~182354 and HD~176209 at frequencies consistent with them being subgiants or contaminated with flux from red giants.

@@

@@

BP acknowledges being on the traditional territory of the Lenape Nations and recognizes that Manhattan continues to be the home to many Algonkian peoples. We give blessings and thanks to the Lenape people and Lenape Nations in recognition that we are carrying out this work on their indigenous homelands. We would like to acknowledge the Gadigal Clan of the Eora Nation as the traditional owners of the land on which the University of Sydney is built and on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.
